A fast unified model for parsing and sentence understanding

### 2016-03-18 writing/hard_stack_paper/paper.tex
Simplify redundant sentence and save a line

A wide range of current models in NLP are built around a neural network component that produces vector representations of sentence meaning \citep{tai2015improved,sutskever2014sequence}. This component, the sentence encoder, is generally formulated as a learned parametric function from a sequence of word vectors to a sentence vector, and this function can take a range of different forms. Common sentence encoders include sequence-based recurrent neural network models (RNNs, see Figure~\ref{fig:batching:good}) with Long Short-Term Memory \citep[LSTM,][]{hochreiter1997long}, which accumulate information over the sentence sequentially, convolutional neural networks over words or characters \citep{kalchbrenner2014convolutional,DBLP:journals/corr/ZhangZL15}, which accumulate information using filters over short local sequences of words, and tree-structured recursive neural networks \citep[TreeRNNs,][see Figure~\ref{fig:batching:bad}]{goller1996learning,socher2011parsing}, which propagate information up a binary parse tree.

>>>>

A wide range of current models in NLP are built around a neural network component that produces vector representations of sentence meaning \citep{tai2015improved,sutskever2014sequence}. This component, the sentence encoder, is generally formulated as a learned parametric function from a sequence of word vectors to a sentence vector, and this function can take a range of different forms. Common sentence encoders include sequence-based recurrent neural network models (RNNs, see Figure~\ref{fig:batching:good}) with Long Short-Term Memory \citep[LSTM,][]{hochreiter1997long}, which accumulate information over the sentence sequentially, convolutional neural networks \citep{kalchbrenner2014convolutional,DBLP:journals/corr/ZhangZL15}, which accumulate information using filters over short local sequences of words or characters, and tree-structured recursive neural networks \citep[TreeRNNs,][see Figure~\ref{fig:batching:bad}]{goller1996learning,socher2011parsing}, which propagate information up a binary parse tree.
